Network Configuration Synthesis with Abstract Topologies

### 2016-11-10 paper/abstraction/paper.tex
update to correct template

\documentclass{sig-alternate-10pt}
%\documentclass[10pt]{sigalternate052015}

@@

@@

\author{%
Ryan Beckett\\
  \affaddr{Princeton}
  %\\
  %\email{rbeckett@princeton.edu}
\and
Ratul Mahajan\\
  \affaddr{Microsoft}
  %\\
  %\email{ratul@microsoft.com}
\and
Todd Millstein\\
  \affaddr{UCLA}
  %\affaddr{University of California, Los Angeles}
  %\\
  %\email{todd@cs.ucla.edu}
\and
Jitendra Padhye\\
  \affaddr{Microsoft}
  %\\
  %\email{padhye@microsoft.com}
\and
David Walker\\
  \affaddr{Princeton}
  %\\
  %\email{dpw@princeton.edu}
}

@@

  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& d_1 : ({ns}_1, d_2) \rightarrow ({ns}_2, d_3) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
  \end{array} \]%

@@

%=====================================================
%
%
%  **Implementation**
%
%
%=====================================================

\section{Implementation}
\label{sec:implementation}

@@

%The compiler performs the following to improve its performance.
%
%\para{Z3 memoization}

@@

%\para{Fast Substitution}
%
%Substitution after compiling a policy abstractly can be expensive since each router must substitute all template variables for each of its connected peers. In practice, because many routers often share the same concrete peers, memoizing the substitution function greatly improves performance.

%=====================================================
%
%
%  **Evaluation**
%
%
%=====================================================

\section{Evaluation}
\label{sec:evaluation}

We apply \sysname on policies for backbone and datacenter networks. We aim to evaluate the expressiveness of our abstract multiplicity annotations, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.

@@

\bibliographystyle{abbrv}
\bibliography{references}

>>>>

\documentclass[numbers, 10pt, preprint]{sigplanconf}
%\documentclass[10pt]{sigalternate052015}

@@

\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country}
\copyrightyear{20yy}
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm}
\copyrightdoi{nnnnnnn.nnnnnnn}

\titlebanner{DRAFT -- do not distribute}        % These are ignored unless
\preprintfooter{submission for PLDI 2017}   % 'preprint' option specified.

@@

%\authorinfo{Ryan Beckett \and David Walker}{Princeton}{}
%\authorinfo{Ratul Mahajan \and Jitendra Padhye}{Microsoft}{}
%\authorinfo{Todd Millstein}{UCLA}{}

\authorinfo{}{}{}

%\author{%
%Ryan Beckett\\
%  \affaddr{Princeton}
%  %\\
%  %\email{rbeckett@princeton.edu}
%\and
%Ratul Mahajan\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{ratul@microsoft.com}
%\and
%Todd Millstein\\
%  \affaddr{UCLA}
%  %\affaddr{University of California, Los Angeles}
%  %\\
%  %\email{todd@cs.ucla.edu}
%\and
%Jitendra Padhye\\
%  \affaddr{Microsoft}
%  %\\
%  %\email{padhye@microsoft.com}
%\and
%David Walker\\
%  \affaddr{Princeton}
%  %\\
%  %\email{dpw@princeton.edu}
%}

@@

  \begin{minipage}[t]{.46\linewidth}
  \hdr{ABGP Syntax}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     abgp &::=& l_1 \rightarrow {rc}_1, ~\dots,~ l_k \rightarrow {rc}_k & \textit{abgp policy} \\
     rc   &::=& t_1 \rightarrow {pc}_1, ~\dots,~ t_k \rightarrow {pc}_k & \textit{router config} \\
     pc   &::=& ma_1, \dots, ma_k & \textit{prefix config} \\
     ma   &::=& lp : ({ns}_1, c_1) \rightarrow ({ns}_2, c_2) & \textit{match action} \\
     ns   &::=& \{ l_1, ~\dots,~ l_k \} & \textit{peers} \\
     t    &::=& \$x \BNFALT d.d.d.d/[d..d] & \textit{predicate} \\
     c    &   & & \textit{community value} \\
     lp   &   & & \textit{local preference} \\
  \end{array} \]%

@@

%=====================================================
%
%
%  **Implementation and Evaluation**
%
%
%=====================================================

\section{Implementation and Evaluation}
\label{sec:evaluation}

@@

@@

To evaluate \sysname, we apply it on policies for backbone and datacenter networks. We aim to evaluate the expressiveness of our abstract multiplicity annotations, the precision of the abstract disjoint-path analysis, and the compilation time of \sysname both with abstraction and without.

@@

\bibliographystyle{abbrvnat}
\bibliography{references}
